The Globular Cluster System of the Auriga Simulations

### 2019-05-12 AurigaGCS.tex
Minor revisions to Sec. 3 (switched to non-mass-weigthed age distribution of MW/M31 GCS). Finished 4.1, near-finished 4.2, and some progress on 4.3

% Abstract of the paper
\begin{abstract}
\todo[inline]{Rob Grand: `for many Auriga papers Carlos Frenk and Adrian Jenkins
are offered co-authorship. Perhaps you could ask Simon about this.'}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way globular cluster population available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. We investigate wether these differences
could result from formation insitu vs. accreted star particles. We find ... TODO.
Furthermore we test whether any of the Auriga galaxies has a metallicity and radial
distribution that is consistent with the MW (M31) GCS. For all of the Auriga haloes
we reject the null hypothesis that the simulated and observed metallicities are
drawn from the same distribution at the 99.99\% confidence level, for the GCS
of the Milky Way as well as that of the Andromeda galaxy. The same holds true for
the distribution of galactocentric radius.
\end{abstract}

@@

\section{Observational data}
\label{sec:observations}
We summarise relevant observations of the globular cluster system of the Milky
Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
have since been discovered by various authors. The total confirmed number of GCs
in the MW adds up to 216 with new estimates now anticipating an additional thirty
GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.

\citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
available data, presented in their CatClu catalog. Amongst 10978 star clusters
and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
candidates. The CatClu catalog contains reference papers, positions, distances,
and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
other quantities, but we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.

Specifically, the relevant data fields that we use from H96e10 are the
metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}.

\subsubsection{Age estimates}
We supplement H96e10 with age-estimates from isochrone fits to stars
near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and
the dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr.

@@

% \todo[inline]{
% ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the
% given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$,
% e.g. Strader, Caldwell \& Seth 2011).''
% }

\subsubsection{Age estimates}
For M31 we find an age distribution with a mean value of 11.0$\pm 0.2$~Gyr and a
dispersion of $2.2$~Gyr. Furthermore, $24$ GCs have age-estimates below $10$~Gyr, and
the minimum age is $4.8$~Gyr.

We present a mass-weighted histogram of the age-estimates of the $55$ MW GCs in V13
and $85$ GCs in M31 for which age-estimates are available in CR16, see
Figure~\ref{fig:MW-M31-age}.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
    \caption{
        Mass-weighted age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 85 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10, but the galactocentric radius
of GCs in M31 is not available in CR16. Therefore we follow
\citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
$(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
We compare these observations to the Auriga simulations later on in
Sec.~\ref{sec:discussion_FeHRgc},

@@

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces 
metallicity distributions consistent with the MW (M31) GC system, and whether 
the subgrid generates sufficient total mass at metallicities (and radii) typical
for the MW (M31) GCS.

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-21_FeH_cleaner-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show 
        the the GG candicates in green. We split the GC candidates into two 
        subpopulations, those that have formed insitu (blue), and those that have 
        been accreted (red). The thin green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system 
        of the MW (M31). \emph{Right:} Total mass in each metallicity bin.
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution 
of Au4-10\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
level (4) and halo number (10 - indicating which set of initial conditions was 
used the run).} and Au4-21, showing the GC candidates in green. The accreted GC 
candidates are shown in red, and the insitu subpopulation in blue. The top panels 
show the MW (M31) GC system in purple (magenta). We overplot a double Gaussian 
for the MW GCS (the purple dashed lines), adopting literature values of the 
mean $\mu$ and standard deviation $\sigma$ of the metal-rich and metal-poor 
populations \citep[][p. 38]{Harris2001}.

We find that the age cut lowers the mean metallicity from $\sim 0.0$ to $\sim -0.6$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metalicity of the old insitu 
and old accreted stars for the majority of the simulations is $\sim 0.3$ (e.g.
Au4-21), and $\sim 0.5$ dex for Au4-10, Au4-16, Au4-17, Au4-18 and Au4-22.
This trent is only reversed for Au4-1 and Au4-4, for which the old insitu population
has a lower mean metallicity instead. For Au4-1 we find $\mu = -1.51$ (-0.74) 
for the old insitu (accreted), but the former consists of only 1019 particles 
(with a total mass of 5e7 M\Sun). Overall we find that the simulations produce 
(sub)populations of GC candidates that are more metal-rich than the MW and M31 
GC systems. Moreover, none of the simulations has a population of GC candidates 
with a bimodal metallicity distribution (the green curves).

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each cross represents one simulation for a given colour. The green (blue) 
        [red] crosses show the values calculated using the old (old insitu) 
        [old accreted] star particles. Green triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
        solid (open) dots indicate the literature values of a bimodal Gaussian 
        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the 
purple (magenta) cross, which shows the mean value of all MW (M31) GCs. 
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of Au4-10 to the MW GCS. In this 
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of Au4-13,
Au4-15, and Au4-17 ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
and 98.32~\%). Here we find that the cumulative distributions are more or less 
similar up to [Fe/H]~$\sim$~-0.5, above which the simulations yield higher number 
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich 
than the MW (M31) GCS because under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5, are the main reason reasons
that $H_0$ is rejected with such high confidence.

In addition, we show the metal-rich (metal-poor) population of the MW GCS using 
a solid (open) dot. The mean metallicities of the old insitu populations appear
roughly consistent with that of the metal-rich population of the MW, but the 
simulations show larger dispersions.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate
the $1\sigma$ interval around it (i.e. scatter between runs with different initial
conditions which thus have unique merger histories). We notice again that
the peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
compared to all stars (green dotted) while the mass at the peak lowers by 
roughly one dex. The mass budget of the old stars is
dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
in purple (magenta) and we show the ratio of the simulated to the observed 
profiles in the middle (bottom) panel. This mass excess can be thought of as a
combination of the bound cluster formation efficiency and disruptive processes,
further discussed in Sec.~\ref{sec:discussion_mass_excess}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS 
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
radial distribution of star particles in all Auriga L4 simulations. We notice 
that the old insitu populations are much more centrally distributed, whereas
the old accreted component has a larger radial extent. Moreover, the dispersion
increases with increasing mean value of the radial distribution.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the old star particles, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furtermore, we find that the dominant contribution to the total mass in old
stars changes from those formed insitu to the accreted population around 
$10$~kpc. We further discuss our comparison between the simulations and the 
observations in Sec.~\ref{sec:discussion_Rgc}.

@@

We investigate whether the Auriga simulations still produce sufficient mass in 
old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
each bin and then divide it by the total mass in the MW (M31) GCS. We show this
mass excess in Figure~\ref{}, respectively Figure~\ref{}
\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}

>>>>

% Abstract of the paper
\begin{abstract}
\todo[inline]{Rob Grand: `for many Auriga papers Carlos Frenk and Adrian Jenkins
are offered co-authorship. Perhaps you could ask Simon about this.'}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way globular cluster population available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. We investigate whether these differences
could result from formation insitu vs. accreted star particles. We find ... TODO.
Furthermore we test whether any of the Auriga galaxies has a metallicity and radial
distribution that is consistent with the MW (M31) GCS. For all of the Auriga haloes
we reject the null hypothesis that the simulated and observed metallicities are
drawn from the same distribution at $\geq98.32$~\% confidence level, for the GCS
of the Milky Way as well as that of the Andromeda galaxy. The same holds true for
the distribution of galactocentric radius.
\end{abstract}

@@

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway}, 
and of the Andromeda (M31) GCS in Sec.~\ref{sec:andromeda}

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
have since been discovered by various authors. The total confirmed number of GCs
in the MW adds up to 216 with new estimates now anticipating an additional thirty
GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be 
53-72\% complete. Specifically, the relevant data fields that we use from H96e10 
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}.

% \citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
% available data, presented in their CatClu catalog. Amongst 10978 star clusters
% and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
% candidates. The CatClu catalog contains reference papers, positions, distances,
% and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
% other quantities, but

We supplement the catalogue with age-estimates from isochrone fits to stars
near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and
the dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr.

@@

The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion of $2.2$~Gyr,
and $24$ GCs have age-estimates below $10$~Gyr with a minimum age of $4.8$~Gyr. 
We show a histogram of the age-estimates of the $55$ MW GCs in V13 and $88$ GCs
in M31 for which age-estimates are available in CR16, see Figure~\ref{fig:MW-M31-age}.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \caption{
        Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}
% \begin{figure}
%     \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
%     \caption{
%         Mass-weighted age distribution of 55 GCs in the MW
%         \citep[data from][]{2013ApJ...775..134V} and 85 GCs
%         in M31 \citep[data from][]{2016ApJ...824...42C}.
%         \label{fig:MW-M31-age}
%     }
% \end{figure}

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10 (assuming $R_{\odot}=8.0$~kpc), but 
the galactocentric radius of GCs in M31 is not available in CR16. Therefore we 
follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
$(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$. The observations indicate that 
no GCs with high metallicities are to be expected at large radii (the three bins 
in the upper right corner, both for MW and M31), and relatively few GCs at large 
radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). We compare these observations to the Auriga
simulations later on in Sec.~\ref{sec:results_FeHRgc}.

@@

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces 
metallicity distributions consistent with the MW (M31) GC system, and whether 
the subgrid generates sufficient total mass at metallicities typical for the 
MW (M31) GCS.

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show 
        the GG candicates in green. We split the GC candidates into two 
        subpopulations, those that have formed insitu (blue), and those that have 
        been accreted (red). The dotted green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system 
        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution 
of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
level (4) and halo number (10 - indicating which set of initial conditions was 
used the run).} and \mbox{Au4-21}, showing the GC candidates in green. The accreted GC 
candidates are shown in red, and the insitu subpopulation in blue. The top panels 
show the MW (M31) GC system in purple (magenta). We overplot a double Gaussian 
for the MW GCS (the purple dashed lines), adopting literature values of the 
mean $\mu$ and standard deviation $\sigma$ of the metal-rich and metal-poor 
populations \citep[][p. 38]{Harris2001}.

We find that the age cut lowers the mean metallicity from \textasciitilde{}$0.0$
to \textasciitilde{}$-0.6$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metallicity of the old insitu 
and old accreted stars for the majority of the simulations is \textasciitilde{}$0.3$ (e.g.
\mbox{Au4-21}), and \textasciitilde{}$0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity 
instead. For \mbox{Au4-1} we find $\mu = -1.51$ (-0.74) for the old insitu (accreted), 
but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and 
with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is 
flawed for this halo due to misclassification of the primary halo in the merger
tree by subfind. For \mbox{Au4-4}, $10.8$ \% of the GC candidates is classified 
as insitu (compared to insitu fractions of $40-80$\% for other haloes). Overall
we find that the simulations produce (sub)populations of GC candidates that are
more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
has a population of GC candidates with a bimodal metallicity distribution
(the green curves).

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue) 
        [red] crosses show the values calculated using the old (old insitu) 
        [old accreted] star particles. Green triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (which would be appropriate for a unimodal 
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the 
purple (magenta) cross, which shows the mean value of all MW (M31) GCs. 
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this 
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
and 98.32~\%). Here we find that the cumulative distributions are more or less 
similar up to [Fe/H]~\textasciitilde{}$-0.5$, above which the simulations yield higher number 
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich 
than the MW (M31) GCS. The main reason reasons that $H_0$ is rejected with such 
high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5.

In addition, we show the metal-rich (metal-poor) population of the MW GCS using 
a solid (open) dot. The mean metallicities of the old insitu populations appear
roughly consistent with that of the metal-rich population of the MW, but the 
simulations show larger dispersions. We are uncertain whether definitive consensus 
is reached concerning uni- or bimodality in the [Fe/H] distribution of M31, but
CR16 argues that the data, after removal of younger objects due to improved age
classification, leans towards unimodality. Therefore we do not show two data
points for the M31 GCS.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the total mass in GC candidates produced by the Auriga simulations. 
We show the median (coloured lines) for all thirty Auriga L4 haloes with the 
$1\sigma$ interval around it (shaded regions, which shows the scatter between 
runs that have different initial conditions, thus, have unique merger histories). 
We chose to aggregate the data to indicate a general trend that we find when the
GC candidates are split up according to birth location, rather than selecting 
typical examples of individual galaxies. Figure~\ref{fig:FeH} shows the mass-weighted
metallicity distribution of all Auriga L4 galaxies. Once again we notice that the 
peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
compared to all stars (green dotted), and we learn that the mass at the peak 
lowers by roughly one dex. The mass budget of the old stars is dominated by the 
old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted 
stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta) 
and we show the ratio of the simulated to the observed profiles in the middle 
(bottom) panel. This mass excess can be thought of the `mass budget' that the
Auriga GC candidates can `afford to lose' due to a combination of smaller than
unity bound cluster formation efficiencies combined with a Hubble time of dynamical 
evolution, while still producing a GC system with sufficient mass to be consistent
with the MW (M31) GCS. The cluster formation efficiency would have to linearly
decrease with decreasing metallicity for Auriga GC candidates to produce a population
of GC candidates that is consistent with the MW. For the GC candidates in M31
we find a constant mass excess up to \textasciitilde{}$-0.9$, above which the 
simulations produce a higher mass excess with increasing metallicity. If dynamical
evolution is not expected to more efficiently disrupt GCs of higher metallicity,
then we would find that the efficiency to form bound star clusters would have to
decrease with increasing metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS 
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
radial distribution of star particles in all Auriga L4 simulations. We notice 
that the old insitu populations are much more centrally distributed, whereas
the old accreted component has a larger radial extent. Moreover, the dispersion
increases with increasing mean value of the radial distribution as may be expected
for a quantity that cannot have negative values.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed insitu to the accreted population around 
$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass excess with increasing radius 
in the range $0.2$ to \textasciitilde{}$5$ kpc, followed by an increase attributed
to the accreted subpopulation. We further investigate a breakdown of the total mass
in Auriga GC candidates into bins of both metallicity and radius in the following
section.

@@

We investigate whether the Auriga simulations still produce sufficient mass when 
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{GC}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to 
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total 
mass in the MW (M31) GCS to obtain the median mass excess produced by the star 
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc} for mass excess with respect to the MW (M31) GCS.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}
